msre design

### 2018-08-19 report/msredesign.tex
removed author, added table of dimensions, and minor changes

\usepackage{graphicx}
\usepackage[figurename=figure]{caption}
\usepackage[autostyle]{csquotes}
\usepackage[style=authoryear,backend=biber]{biblatex}
\addbibresource{msredesign.bib}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
}
\urlstyle{same}

\title{msre design}
\author{aslak stubsgaard}
\date{}

@@

\subsection{control rod and sample assembly}
the control rod and sample assembly is further detailed in figure \ref{61246-fig14a}, \ref{61246-fig14b}, and \ref{61246-fig14c}.
\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=23,width=0.8\textwidth,trim={4cm 2cm 4.8cm 2cm},clip]{./references/AD-CF-61-2-46.pdf}}
  \caption{msre control rod arrangement \parencite[figure 14a]{ad-cf-61-2-46}.}
  \label{61246-fig14a}
\end{figure}
% \begin{figure}[H]
%   \fbox{\includegraphics[page=10,width=0.8\textwidth,trim={3cm 9.5cm 3.5cm 8cm},clip]{./references/ORNL-TM-0378.pdf}}
%   \caption{msre control rod arrangements and typical fuel channels \parencite[figure 2]{ornl-tm-0378}.}
%   \label{0378-fig2}
% \end{figure}

>>>>

\usepackage{graphicx}
\usepackage[figurename=figure,tablename=table]{caption}
\usepackage[autostyle]{csquotes}
\usepackage[style=authoryear,backend=biber]{biblatex}
\addbibresource{msredesign.bib}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black
}
\urlstyle{same}

\title{msre design}
\author{}
\date{}

@@

table \ref{61246-tab4} gives many of the key dimensions left out of the figures \ref{3229-fig1} and \ref{0378-fig1}.
\begin{table}[H]
  \centering
  \caption{reactor vessel design data \parencite[table 4]{ad-cf-61-2-46}.}
  \fbox{\includegraphics[page=11,width=0.8\textwidth,trim={2cm 3.5cm 2cm 3.5cm},clip]{./references/AD-CF-61-2-46.pdf}}
  \label{61246-tab4}
\end{table}

% \begin{table}[H]
%   \centering
%   \caption{properties of msre core graphite \parencite[table 3]{ad-cf-61-2-46}.}
%   \fbox{\includegraphics[page=9,width=0.8\textwidth,trim={2cm 4cm 2cm 3.4cm},clip]{./references/AD-CF-61-2-46.pdf}}
%   \label{61246-tab3}
% \end{table}

\subsection{control rod and sample assembly}
the control rod and sample assembly is further detailed in figure \ref{61246-fig14a}, \ref{61246-fig14b}, and \ref{61246-fig14c}.
\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=23,width=0.8\textwidth,trim={4cm 2cm 4.8cm 2cm},clip]{./references/AD-CF-61-2-46.pdf}}
  \caption{msre control rod arrangement \parencite[figure 14a]{ad-cf-61-2-46}.}
  \label{61246-fig14a}
\end{figure}
